---
title: "Question 3 -KNN"
author: "Anil Akyildirim"
date: "3/29/2020"
output:
  html_document: default
  pdf_document: default
---

```{r}
#load dataset
library(tidyverse)
knn.data <- read.csv("icu.csv")
head(knn.data)



```

```{r}
#look to see datatypes
str(knn.data)

```

```{r}
# create COMA feature
knn.data <- mutate(knn.data, COMA=ifelse(LOC==2, 1, 0))
head(knn.data)

```

```{r}
# change class from numerical to categorical
unique(knn.data$STA)
knn.data$STA <- factor(knn.data$STA)

```




```{r}
# keep 5 features
features <- c('TYP', 'AGE', 'INF', 'COMA', 'STA')
knn.df <- knn.data[features]
head(knn.df)

```


```{r}
euclideanDist <- function(a, b){
  d = 0
  for(i in c(1:(length(a)) ))
  {
    d = d + (a[[i]]-b[[i]])^2
  }
  d = sqrt(d)
  return(d)
}

knn_predict2 <- function(test_data, train_data, k_value, labelcol){
  pred <- c()  #empty pred vector 
  #LOOP-1
  for(i in c(1:nrow(test_data))){   #looping over each record of test data
    eu_dist =c()          #eu_dist & eu_char empty  vector
    eu_char = c()
    good = 0              #good & bad variable initialization with 0 value
    bad = 0
    
    #LOOP-2-looping over train data 
    for(j in c(1:nrow(train_data))){
 
      #adding euclidean distance b/w test data point and train data to eu_dist vector
      eu_dist <- c(eu_dist, euclideanDist(test_data[i,-c(labelcol)], train_data[j,-c(labelcol)]))
 
      #adding class variable of training data in eu_char
      eu_char <- c(eu_char, as.character(train_data[j,][[labelcol]]))
    }
    
    eu <- data.frame(eu_char, eu_dist) #eu dataframe created with eu_char & eu_dist columns
 
    eu <- eu[order(eu$eu_dist),]       #sorting eu dataframe to gettop K neighbors
    eu <- eu[1:k_value,]               #eu dataframe with top K neighbors
 
    tbl.sm.df<-table(eu$eu_char)
    cl_label<-  names(tbl.sm.df)[[as.integer(which.max(tbl.sm.df))]]
    
    pred <- c(pred, cl_label)
    }
    return(pred) #return pred vector
  }
  

accuracy <- function(test_data,labelcol,predcol){
  correct = 0
  for(i in c(1:nrow(test_data))){
    if(test_data[i,labelcol] == test_data[i,predcol]){ 
      correct = correct+1
    }
  }
  accu = (correct/nrow(test_data)) * 100  
  return(accu)
}


```

```{r}
#load data
labelcol <- 5 # for df it is the fifth col 
predictioncol<-labelcol+1

```

```{r}

# create train/test partitions
set.seed(2)
n<-nrow(knn.df)
knn.df<- knn.df[sample(n),]

train.df <- knn.df[1:as.integer(0.7*n),]

```



```{r}

K = 3 # number of neighbors to determine the class
table(train.df[,labelcol])
test.df <- knn.df[as.integer(0.7*n +1):n,]
table(test.df[,labelcol])
predictions <- knn_predict2(test.df, train.df, K,labelcol) #calling knn_predict()
test.df[,predictioncol] <- predictions #Adding predictions in test data as 7th column
print(accuracy(test.df,labelcol,predictioncol))
table(test.df[[predictioncol]],test.df[[labelcol]])
accuracy_score_3 <- accuracy(test.df,labelcol,predictioncol) # create accuracy score object for further plotting
```

Above outlines the confusion MAtrix and accuracy score(76.67) when K is 3.

```{r}

K = 5 # number of neighbors to determine the class
table(train.df[,labelcol])
test.df <- knn.df[as.integer(0.7*n +1):n,]
table(test.df[,labelcol])
predictions <- knn_predict2(test.df, train.df, K,labelcol)
test.df[,predictioncol] <- predictions #Adding predictions in test data as 7th column
print(accuracy(test.df,labelcol,predictioncol))
table(test.df[[predictioncol]],test.df[[labelcol]])
accuracy_score_5 <- accuracy(test.df,labelcol,predictioncol) # create accuracy score object for further plotting

```

Above outlines the confusion Matrix and accuracy(80) when K is 5.

```{r}
K = 7 # number of neighbors to determine the class
table(train.df[,labelcol])
test.df <- knn.df[as.integer(0.7*n +1):n,]
table(test.df[,labelcol])
predictions <- knn_predict2(test.df, train.df, K,labelcol)
test.df[,predictioncol] <- predictions #Adding predictions in test data as 7th column
print(accuracy(test.df,labelcol,predictioncol))
table(test.df[[predictioncol]],test.df[[labelcol]])
accuracy_score_7 <- accuracy(test.df,labelcol,predictioncol) # create accuracy score object for further plotting

```

Above is the confusion matrix and accuracy score for K=7.

```{r}

K = 15 # number of neighbors to determine the class
table(train.df[,labelcol])
test.df <- knn.df[as.integer(0.7*n +1):n,]
table(test.df[,labelcol])
predictions <- knn_predict2(test.df, train.df, K,labelcol)
test.df[,predictioncol] <- predictions #Adding predictions in test data as 7th column
print(accuracy(test.df,labelcol,predictioncol))
table(test.df[[predictioncol]],test.df[[labelcol]])
accuracy_score_15 <- accuracy(test.df,labelcol,predictioncol) # create accuracy score object for further plotting


```

Above is the confusion matrix and accuracy score for K=15

```{r}

K = 25 # number of neighbors to determine the class
table(train.df[,labelcol])
test.df <- knn.df[as.integer(0.7*n +1):n,]
table(test.df[,labelcol])
predictions <- knn_predict2(test.df, train.df, K,labelcol)
test.df[,predictioncol] <- predictions #Adding predictions in test data as 7th column
print(accuracy(test.df,labelcol,predictioncol))
table(test.df[[predictioncol]],test.df[[labelcol]])
accuracy_score_25 <- accuracy(test.df,labelcol,predictioncol) # create accuracy score object for further plotting
```

Above is the confusion matrix and accuracy score for K=25

```{r}

K = 50 # number of neighbors to determine the class
table(train.df[,labelcol])
test.df <- knn.df[as.integer(0.7*n +1):n,]
table(test.df[,labelcol])
predictions <- knn_predict2(test.df, train.df, K,labelcol)
test.df[,predictioncol] <- predictions #Adding predictions in test data as 7th column
print(accuracy(test.df,labelcol,predictioncol))
table(test.df[[predictioncol]],test.df[[labelcol]])
accuracy_score_50 <- accuracy(test.df,labelcol,predictioncol) # create accuracy score object for further plotting

```

```{r}

accuracy_score <- c(accuracy_score_3, accuracy_score_5, accuracy_score_7, accuracy_score_15, accuracy_score_25, accuracy_score_50)
k_numbers <- c(3,5,7,15,25,50)
plot(k_numbers, accuracy_score)
lines(k_numbers, accuracy_score)

```

TWe selected TYP, AGE and INF as a descriptive variable from our dataset. We created COMA variable with a defined condition and added to the descriptive variables. Our target variable is STA which has two classes (0 and 1). We defined our KNN model from scratch with distance function (iterate, sort , combine) for prediction and we also defined accuracy function. We run the model for K(3,5,7,15,25,50), note the predicted vs real values(confusionmatrix), accuracy for each K and plot of accuracy vs K. We notice that K>7 (15,25,50), even though accuracy is higher, we are getting wrong predicted values. Ideal K value is 7. 



